Quality Assesment of OpenStreetMap Footpath Data for 3D City Modelling

### 2020-05-10 report/report.tex
Update todo
Fix journal sources

% TODO: Algorithm showing the edge projected distance algorithm for the collision study
% TODO: Figure detailing the steps in the point-matching algorithm

% After response from Todor:
% TODO: Write section: Utility in real world applications
% TODO: Spell check
% TODO: Go over report one final time

@@

\bibitem{haklay-10}
(Haklay, 2010), How good is volunteered geographical information?A comparative study of OpenStreetMap and OrdnanceSurvey datasets \\
\href{https://kfrichter.org/crowdsourcing-material/day1/haklay10.pdf}.

\bibitem{fan-14}
(Fan et al, 2014), Quality assessment for building footprints data on OpenStreetMap \\
\href{https://www.researchgate.net/publication/262163378\_Quality\_assessment\_for\_building\_footprints\_data\_on\_OpenStreetMap}.

\bibitem{arkin-91}
Arkin E.M., Chew L.P., Huttenlocher D.P., Kedem K. and Mitchell J.S.B. 1991. An Efficiently Computable \\
Metric for Comparing Polygonal Shapes. In: IEEE Transaction on Pattern Analysis and Machine \\
Intelligence, Vol. 13, No. 3, March 1991. \\

\bibitem{douglas-peucker-73}
Douglas, D.H. and Peucker T.K. 1973. Algorithms for the reduction of the number of points required to \\
represent a digitalized line or its caricature. In: Cartographica: The International Journal for Geographic \\
Information and Geovisualization, 10(2), 112-122. \\

\bibitem{rutzinger-09}
Rutzinger, M., Rottensteiner, F. and Pfeifer, N. 2009. A Comparison of Evaluation Techniques for Building \\
Extraction From Airborne Laser Scanning. IEEE Journal of Selected Topics in Applied Earth \\
Observations and Remote Sensing 2(1): 11-20. \\

@@

\bibitem{van-oort-06}
van Oort P A J. 2006. Spatial Data Quality: From Description to Application. PhD Thesis, Wageningen University.

\bibitem{kunze-12}
Kunze, C. 2012. Vergleichsanalyse des Gebäudedatenbestandes aus OpenStreetMap mit amtlichen Datenquellen. \\
Student research project at the Technical University of Dresden, online avaiable: http://nbn- \\
resolving.de/urn:nbn:de:bsz:14-qucosa-88141

>>>>

% After response from Todor:
% TODO: Write section: Utility in real world applications

% After wednesday meeting with Chris
% TODO: Algorithm showing the edge projected distance algorithm for the collision study
% TODO: Figure detailing the steps in the point-matching algorithm
% TODO: Spell check
% TODO: Go over report one final time

@@

\bibitem{haklay-10}
Haklay, M. (2010). How Good is Volunteered Geographical Information? A Comparative Study of OpenStreetMap and Ordnance Survey Datasets. Environment and Planning B: Planning and Design, 37(4), 682–703.

\bibitem{fan-14}
Fan, Hongchao \& Zipf, Alexander \& Fu, Qing \& Neis, Pascal. (2014). Quality assessment for building footprints data on OpenStreetMap. International Journal of Geographical Information Science. 28. 700-719.

\bibitem{arkin-91}
Arkin, Esther \& Chew, L. \& Huttenlocher, Daniel \& Kedem, Klara \& Mitchell, Joseph. (1991). An Efficiently Computable Metric for Comparing Polygonal Shapes. IEEE Transaction Pattern Analysis and Machine Intelligence 13. 209-216.

\bibitem{douglas-peucker-73}
Douglas, D.H. \& Peucker T.K. (1973). Algorithms for the Reduction of the Number of Points Required to Represent a Digitalized Line or Its Caricature. Cartographica: The International Journal for Geographic Information and Geovisualization, 10(2), 112-122.

\bibitem{rutzinger-09}
Rutzinger, M., Rottensteiner, F. and Pfeifer, N. (2009). A Comparison of Evaluation Techniques for Building Extraction From Airborne Laser Scanning. IEEE Journal of Selected Topics in Applied Earth Observations and Remote Sensing 2(1): 11-20.

@@

\bibitem{van-oort-06}
Van Oort P.A.J. (2006). Spatial Data Quality: From Description to Application. PhD Thesis, Wageningen University.

\bibitem{kunze-12}
Kunze, C. (2012). Vergleichsanalyse des Gebäudedatenbestandes aus OpenStreetMap mit amtlichen Datenquellen. Student research project, Technical University of Dresden. http://nbn-resolving.de/urn:nbn:de:bsz:14-qucosa-88141
